%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Employment History}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Student Researcher} % Job title
    {Australian National University} % Organization
    {Canberra, ACT} % Location
    {Jul. 2016 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {PhD project centred on developing a beam combiner for the Pyxis interferometer (see \url{www.mso.anu.edu.au/pyxis} for more information). Have also been involved with the LIFE (Large Interferometer For Exoplanets) initiative (see \url{www.life-space-mission.com}) in simulating nulling interferometry compatible telescope configurations. Interested in the properties of Mira variables using high angular resolution measurements from the CHARA and VLTI interferometric facilities.}
        \item {Honours project with Prof. Michael Ireland in simulating a linear formation flying, space interferometer mission with the aim of detecting biosignatures on exoplanets.}
        \item {Undergraduate projects with Prof. Michael Ireland, Dr Brad Tucker, Dr Tony Travouillon and Dr Luca Casagrande. These varied from tracing back the positions of stars in order to determine cluster membership, to building an instrument designed to measure turbulence inside a telescope dome, to identifying relationships between exoplanets and their host star's properties.}
      \end{cvitems}
    }

  \cventry
    {Outreach Assistant} % Affiliation/role
    {Mount Stromlo Observatory} % Organization/group
    {Canberra, ACT} % Location
    {Apr. 2018 - Oct. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Assisted with the ANU Stargazing World Record Attempt.}
        \item {Regularly give tours and present to school and private groups at Mt Stromlo Observatory.}
        \item {Assisted in giving talks to schools around regional South Australia and local Canberran schools.}
        \item {Given many talks and written newspaper articles about astronomy (see \url{http://www.mso.anu.edu.au/~jhansen/\#outreach})}
      \end{cvitems}
    }
    

%---------------------------------------------------------
  \cventry
    {PhD Intern} % Job title
    {HEO Robotics} % Organization
    {Sydney, NSW} % Location
    {Oct. 2020 - Jan. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Researched and designed an optical payload for a future space situational awareness (SSA) satellite.}
        \item {Purchased and tested a potential optical system, both for optical quality and for survivability in space.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Student Fellowship Holder} % Job title
    {Australian Astronomical Observatory} % Organization
    {Sydney, NSW} % Location
    {Dec. 2017 - Feb. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Conducted a research project with Dr. Barnaby Norris in Adaptive Optics Instrumentation.}
        \item {Designed and tested a photonic lantern based wavefront sensor, designed to increase the speed and accuracy at which atmospheric turbulence can be detected.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Student Ambassador} % Job title
    {Australian National University} % Organization
    {Canberra, ACT} % Location
    {Jan. 2017 -  Jan. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Lead tours of the ANU campus on a fortnightly basis.}
        \item {Team leader for major events, such as ANU Commencement Address and ANU Open Day.}
        \item {Gave presentations to prospective ANU students.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Student Researcher} % Job title
    {Max Planck Institute for Astronomy} % Organization
    {Heidelberg, Germany} % Location
    {Jul. - Aug. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Conducted a research project into galaxy evolution and morphology with Dr Kai Noeske.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
%  \cventry
%    {Work Experience Student} % Job title
%    {Defence Science and Technology Organisation} % Organization
%    {Adelaide, SA} % Location
%    {Apr. 2013} % Date(s)
%    {
%      \begin{cvitems} % Description(s) of tasks/responsibilities
%        \item {Worked on a tactical simulation between a submarine and an aerial assault.}
%      \end{cvitems}
%      %\begin{cvsubentries}
%      %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
%      %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
%      %\end{cvsubentries}
%    }

%---------------------------------------------------------
\end{cventries}
