%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Presentations}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
    \cventry
    {Presenter on the Pyxis Interferometer} % Role
    {9th Australian Exoplanet Workshop 2023} % Event
    {Sydney, Australia} % Location
    {Sep. 2023} % Date(s)
    {}
      \vspace{-0.2cm}  
    
    \cventry
    {Presenter on the Pyxis Interferometer} % Role
    {Astronomical Society of Australia, Annual Science Meeting 2023} % Event
    {Sydney, Australia} % Location
    {Jul. 2023} % Date(s)
    {}
      \vspace{-0.2cm}  
      
       
       \cventry
    {Presenter on the Pyxis Interferometer and Architectures for the Large Interferometer for Exoplanets} % Role
    {Keck Institute For Space Studies Workshop: Exploring Exoplanets With Interferometry} % Event
    {Pasadena, California, USA} % Location
    {Nov. 2022} % Date(s)
    {}
    \vspace{-0.2cm}
      
      \cventry
    {Presenter on the Pyxis Interferometer} % Role
    {20th Australian Space Research Conference} % Event
    {Sydney, Australia} % Location
    {Sep. 2022} % Date(s)
    {}
    \vspace{-0.2cm}
    
       \cventry
    {Presenter on the Pyxis Interferometer (Papers 12183-48 and 12183-49)} % Role
    {Optical and Infrared Interferometry and Imaging VIII, SPIE Astronomical Telescopes and Instrumentation} % Event
    {Montreal, Canada} % Location
    {Jul. 2022} % Date(s)
    {}
    \vspace{-0.2cm}
    
    \cventry
    {Poster presenter on the Pyxis Interferometer} % Role
    {Astronomical Society of Australia, Annual Science Meeting 2022} % Event
    {Hybrid; Melbourne, Australia} % Location
    {Jun. 2022} % Date(s)
    {}
    \vspace{-0.2cm}    
    
    \cventry
    {Poster presenter on the Pyxis Interferometer} % Role
    {Astronomical Society of Australia, Annual Science Meeting 2021} % Event
    {Hybrid; Hobart, Australia} % Location
    {Jul. 2021} % Date(s)
    {}
      \vspace{-0.2cm}  
      
    \cventry
    {Presenter on formation-flying interferometry in low Earth orbit (Paper E1.20-0013-21)} % Role
    {43rd COSPAR Scientific Assembly} % Event
    {Online; Sydney, Australia} % Location
    {Jan. 2021} % Date(s)
    {}
     \vspace{-0.2cm}         
      
  \cventry
    {Poster presenter on formation-flying interferometry in low Earth orbit (Paper 11443-177)} % Role
    {Space Telescopes and Instrumentation 2020: Optical, Infrared, and Millimeter Wave, SPIE Astronomical Telescopes and Instrumentation} % Event
    {Online} % Location
    {Dec. 2020} % Date(s)
    {}
    \vspace{-0.2cm}


%---------------------------------------------------------
\end{cventries}
