%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------

%---------------------------------------------------------
  \cventry
    {Member, Secretary in 2017 \& Treasurer in 2018} % Affiliation/role
    {ANU Physics Society} % Organization/group
    {Australian National University} % Location
    {Jun. 2016 - Nov. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Helped re-affiliate the society after disaffiliation in 2015.}
        \item {Led and organised multiple science based trivia nights.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Pianist/Trumpet Player} % Affiliation/role
    {ANU Music Society} % Organization/group
    {Australian National University} % Location
    {Feb. 2016 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Played in bi-yearly concerts for both a general audience, as well as a pre-kindergarden concert.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Academic Liaison} % Affiliation/role
    {ANU National Science Week Committee} % Organization/group
    {Australian National University} % Location
    {Aug. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Organised and developed a research market day for undergraduates to learn what research is available at ANU.}
        \item {Main contact in finding over 50 academics and PhD students to present their research to students.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Student Volunteer} % Affiliation/role
    {ConocoPhillips Science Experience} % Organization/group
    {Australian National University} % Location
    {Sept. 2016-2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Assisted Year 9 and 10 students by showing them around the ANU campus and encouraging an interest in science.}
      \end{cvitems}
    }


%---------------------------------------------------------
\end{cventries}
